|

### 2023-04-26 manuscript/Chapter2-appendix3.Rmd
update fig titles in appendix3

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared."}

@@

>>>>

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared. The results are from the model that includes the outlier."}

@@

```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis. The results are from the MDHGLM that includes the outlier."}

knitr::include_graphics(
  here::here(
    "outputs", "04_outputs_figures",
    "appendix3_figureS2.png"
  )
)
